### 2019-11-15 cvpr_submission/experiments.tex
Changes in experiments

\section{Experiments}
\label{sec:experiments}
We implemented and trained our SAMNet model using MI-Prometheus~\cite{kornuta2018accelerating}, a framework based on Pytorch~\cite{paszke2017automatic}. We evaluated the model on the COG dataset~\cite{yang2018dataset}, a video reasoning~\cite{mogadala2019trends} dataset developed for the purpose of research on relational and temporal reasoning, as well as on the CLEVR dataset~\cite{johnson2017clevr}, created for Image Question Answering research.
Our experiments were designed to study SAMNet's performance as well as its generalization and transfer learning abilities in different settings.
For the temporal and feature transfer experiments, we used two variants of both datasets.
For COG, an easy one (Canonical) and a Hard variant, differ mainly on the number of frames in the input sequence and number of 
distractors (see~\cref{tab:cog_variants}).
\begin{table}[ht]
	\centering
	\begin{adjustbox}{width=0.45\textwidth}
		\begin{tabular}{lccc}
			\toprule
			Variant	&	Number of frames	&	Max. memory duration	&	Max. number of distractors \\ 
			\midrule
			Canonical & 4 & 3 & 1\\	
			Hard  & 8 & 7 & 10\\
			\bottomrule	
		\end{tabular}
	\end{adjustbox}
	\caption{Details of the Canonical and Hard variants of the COG dataset.}
	\label{tab:cog_variants}
\end{table}
This experiment is described in~\cref{sec:temporal}.
For CLEVR, we consider the CoGenT (Constrained Generalization Test) variant which contains two conditions, differing on the combinations of attributes values.
\Cref{sec:feature} describes this experiment.
For the reasoning transfer experiments, we consider 23 classification tasks in COG and the 5 original question categories in CLEVR.
%More details on the composition of these datasets is available in Appendix \ref{sec:datasets-desc}.

@@

\subsection{Reasoning transfer on CLEVR and COG}
\label{sec:reasoning}
In these experiments using the CLEVR and COG datasets, we focus on analyzing the impact 
of each task relatively to others when training jointly.

\subsubsection{CLEVR}
\label{sec:reasoning-clevr}
For the CLEVR dataset, we consider the question categories defined by the authors: \textit{Exist}, \textit{Count}, \textit{CompareInteger}, \textit{CompareAttribute}, \textit{QueryAttribute} and conducted the following experiments:
\begin{itemize}
	\compresslist
	\item Train and test SAMNet on a single task group $t$. These 5 experiments fit into the traditional Deep Learning procedure of single-task learning,
	\item Train SAMNet on all task groups jointly, and evaluate its performance on each task $t$ separately,
	\item Finally, for each task group $t$, we train SAMNet on all tasks but $t$, and test its performance on $t$. %These experiments steer away from single / multi-task training and rather fall under the Domain Adaptation setting, categorized as \emph{transductive} transfer learning in \cite{pan2009survey}.
\end{itemize}

@@

\subsubsection{COG}
\label{sec:reasoning-cog}
For the COG dataset, the number of tasks (23) is large, so we decided  there is no a priori grouping of tasks

@@

\begin{table}[ht]
	\centering
	\begin{adjustbox}{width=0.45\textwidth}
		\begin{tabular}{lccc}
			\toprule
			Variant	&	Number of frames	&	Max. memory duration	&	Max. number of distractors \\ 
			\midrule
			Canonical & 4 & 3 & 1\\	
			Hard  & 8 & 7 & 10\\
			\bottomrule	
		\end{tabular}
	\end{adjustbox}
	\caption{Details of the Canonical and Hard variants of the COG dataset.}
	\label{tab:cog_variants}
\end{table}\vspace{5pt}

>>>>

\section{Experiments}
\label{sec:experiments}
We implemented and trained our SAMNet model using MI-Prometheus~\cite{kornuta2018accelerating}, a framework based on Pytorch~\cite{paszke2017automatic}. We evaluated the model on the COG dataset~\cite{yang2018dataset}, a video reasoning~\cite{mogadala2019trends} dataset developed for the purpose of research on relational and temporal reasoning, as well as on the CLEVR dataset~\cite{johnson2017clevr}, created for Image Question Answering research.
Our experiments were designed to study SAMNet's performance as well as its generalization and transfer learning abilities in different settings.
For the temporal and feature transfer experiments, we used two variants of both datasets.
For COG, an easy one (Canonical) and a Hard variant, differ mainly on the number of frames in the input sequence,
the maximum amount of look-back in frame history with the relevant information for each frame,  and number of 
distractors (see~\cref{tab:cog_variants}).
\begin{table}[ht]
	\centering
	%\begin{adjustbox}{width=0.45\textwidth}
		\begin{tabular}{lccc}
			\toprule
			Variant	& Frames & History	& Distractors \\ 
			\midrule
			Canonical & 4 & 3 & 1\\	
			Hard  & 8 & 7 & 10\\
			\bottomrule	
		\end{tabular}
	%\end{adjustbox}
	\caption{Details of the Canonical and Hard variants of COG}
	\label{tab:cog_variants}
\end{table}
This experiment is described in~\cref{sec:temporal}.
For CLEVR, we consider the CoGenT (Constrained Generalization Test) variant which contains two conditions, differing on the combinations of attributes values.
\Cref{sec:feature} describes this experiment.
For the reasoning transfer experiments, we consider 23 classification tasks in COG and the 5 original question categories in CLEVR.
%More details on the composition of these datasets is available in Appendix \ref{sec:datasets-desc}.

@@

\subsection{Reasoning transfer on CLEVR and COG}
\label{sec:reasoning}
In these experiments using the CLEVR and COG datasets, we focus on analyzing the impact 
of each task relatively to others when training jointly.
For each dataset, we defined appropriate task families that reflect the characteristics of that dataset and designed
appropriate experiments to study the effectiveness of transfer learning across task families.

\subsubsection{CLEVR}
\label{sec:reasoning-clevr}
For the CLEVR dataset, we consider the question categories defined by the authors: \textit{Exist}, \textit{Count}, \textit{CompareInteger}, \textit{CompareAttribute}, \textit{QueryAttribute} and conducted the following experiments:
\begin{itemize}
	\item Train and test SAMNet on a single task group $t$. These 5 experiments fit into the traditional ML setup of single-task learning;
	\item Train SAMNet on all task groups jointly and evaluate its performance on each task group $t$ separately.
	This is a transfer learning setting where for the source task family, the task is sampled from all questions,
	while for the target task family, the samples consist of questions from group $t$ only;
	\item Finally, for each task group $t$, we train SAMNet on all tasks but $t$, and test its performance on $t$.
	This can also be viewed as a transfer learning setting similar to the previous case.
	%These experiments steer away from single / multi-task training and rather fall under the Domain Adaptation setting, categorized as \emph{transductive} transfer learning in \cite{pan2009survey}.
\end{itemize}

@@

\subsubsection{COG}
\label{sec:reasoning-cog}
For the COG dataset, the number of task groups (23) is large, so we designed a 2-level hierarchy of the task groups motivated by the
description of these tasks.

@@
